### 2013-07-10 latex/paper-PLOS_ONE-revised.tex
Uncomment figures, modified Acknowledgment
Preparing everything for resubmission.

%\section*{Acknowledgments}
%This work was supported by NIH grant R01 GM088344 to C.O.W.

\bibliography{bibliography}

@@

\begin{figure}[H]
\includegraphics[width=4in]{figures/Figure1.pdf}
\caption{\label{fig:BarGraphRSA}Frequency of residues with $\text{RSA}>1$ in empirical protein structures. Nearly all amino acids, and notably R, D, K, G, and P, show $\text{RSA}>1$ 
when RSA is calculated using the normalization values of either Rose \emph{et al.} \cite{Rose1985} or Miller \emph{et al.} \cite{Miller1987}.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=3in]{figures/Figure2.pdf}
\caption{\label{fig:RamaAla}Ramachandran plot for alanine residues in our empirical data set. Coordinates which correspond to RSA values $>1$ are shown in red and are clearly concentrated around coordinates $(-50^\circ,-45^\circ)$. We therefore propose that this region contains the maximally exposed conformation of alanine and should be used for calculating maximum SA.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=6in]{figures/Figure3.pdf}
\caption{\label{fig:heatrama} Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All bins in the ALLOWED region are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for non-empty bins in (A). Both the empirical and the theoretical approach find the largest SA values in the $\alpha$-helix region around $(-50^\circ,-45^\circ)$. By contrast, the extended conformation $(-120^\circ, 140^\circ)$ leads to relatively low maximum SA.}
\end{figure}

\begin{figure}[H]
\includegraphics[width=3in]{figures/Figure4.pdf}
\caption{\label{fig:EvC} Difference between theoretically and empirically determined maximum SA values for alanine, across $5^\circ$ by $5^\circ$ bins. As the amount of data per bin increases, the difference between theoretical and empirical maximum SA approaches zero, demonstrating that our two methods converged with increasing amounts of data. Furthermore, the difference between values is frequently close to zero, even when little data is available for a bin. This observation indicates that our theoretically derived maximum SA values provide a tight bound on the empirically observed ones.}
\end{figure}

>>>>

\section*{Acknowledgments}
%This work was supported by NIH grant R01 GM088344 to C.O.W.
We thank Jeff Gray for insightful discussions on this work.

%\bibliography{bibliography}

\begin{thebibliography}{10}
\providecommand{\url}[1]{\texttt{#1}}
\providecommand{\urlprefix}{URL }
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi
\providecommand{\bibAnnoteFile}[1]{%
  \IfFileExists{#1}{\begin{quotation}\noindent\textsc{Key:} #1\\
  \textsc{Annotation:}\ \input{#1}\end{quotation}}{}}
\providecommand{\bibAnnote}[2]{%
  \begin{quotation}\noindent\textsc{Key:} #1\\
  \textsc{Annotation:}\ #2\end{quotation}}
\providecommand{\eprint}[2][]{\url{#2}}

\bibitem{Chothia1976}
Chothia C (1976) The nature of the accessible and buried surfaces in proteins.
\newblock J Mol Biol : 1--14.
\bibAnnoteFile{Chothia1976}

\bibitem{Rose1985}
Rose GD, Geselowitz AR, Lesser GJ, Lee RH, Zehfus MH (1985) Hydrophobicity of
  amino acid residues in globular proteins.
\newblock Science 229: 834--838.
\bibAnnoteFile{Rose1985}

\bibitem{Miller1987}
Miller S, Janin J, Lesk AM, Chothia C (1987) Interior and surface of monomeric
  proteins.
\newblock J Mol Biol 196: 641--656.
\bibAnnoteFile{Miller1987}

\bibitem{Moelbert2004}
Moelbert S, Emberly E, Tang C (2004) Correlation between sequence
  hydrophobicity and surface-exposure pattern of database proteins.
\newblock Prot Sci : 752--762.
\bibAnnoteFile{Moelbert2004}

\bibitem{Shaytan2009}
Shaytan AK, Shaitan KV, Khokhlov AR (2009) Solvent accessible surface area of
  amino acid residues in globular proteins: Correlations of apparent transfer
  free engergies with experimental hydrophobicity scales.
\newblock Biomacromolecules 10: 1224--1237.
\bibAnnoteFile{Shaytan2009}

\bibitem{Goldmanetal1998}
Goldman N, Thorne JL, Jones DT (1998) Assessing the impact of secondary
  structure and solvent accessibility on protein evolution.
\newblock Genetics 149: 445--458.
\bibAnnoteFile{Goldmanetal1998}

\bibitem{Bloometal2006}
Bloom JD, Drummond DA, Arnold FH, Wilke CO (2006) Structural determinants of
  the rate of protein evolution in yeast.
\newblock Mol Biol Evol 23: 1751--1761.
\bibAnnoteFile{Bloometal2006}

\bibitem{FranzosaXia2009}
Franzosa EA, Xia Y (2009) Structural determinants of protein evolution are
  context-sensitive at the residue level.
\newblock Mol Biol Evol 26: 2387--2395.
\bibAnnoteFile{FranzosaXia2009}

\bibitem{Zhouetal2009}
Zhou T, Weems M, Wilke CO (2009) Translationally optimal codons associate with
  structurally sensitive sites in proteins.
\newblock Mol Biol Evol 26: 1571--1580.
\bibAnnoteFile{Zhouetal2009}

\bibitem{FranzosaXia2012}
Franzosa EA, Xia Y (2012) Independent effects of protein core size and
  expression on structure-evolution relationships at the residue level.
\newblock PLoS One 7: e46602.
\bibAnnoteFile{FranzosaXia2012}

\bibitem{Scherrer2012}
Scherrer MP, Meyer AG, Wilke CO (2012) Modeling coding-sequence evolution
  within the context of residue solvent accessibility.
\newblock BMC Evol Biol 12: 179.
\bibAnnoteFile{Scherrer2012}

\bibitem{MeyerWilke2012}
Meyer AG, Wilke CO (2012) Integrating sequence variation and protein structure
  to identify sites under selection.
\newblock Mol Biol Evol .
\bibAnnoteFile{MeyerWilke2012}

\bibitem{ConantStadler2009}
Contant GC, Stadler PF (2009) Solvent exposure imparts similar selective
  pressures across a range of yeast proteins.
\newblock Mol Biol Evol 26: 1155--1161.
\bibAnnoteFile{ConantStadler2009}

\bibitem{RostSander1994}
Rost B, Sander C (1994) Conservation and prediction of solvent accessibility in
  protein families.
\newblock Proteins 20: 216--226.
\bibAnnoteFile{RostSander1994}

\bibitem{Pollastrietal2002}
Pollastri G, Baldi P, Fariselli P, Casadio R (2002) Prediction of coordination
  number and relative solvent accessibility in proteins.
\newblock Proteins 47: 142--153.
\bibAnnoteFile{Pollastrietal2002}

\bibitem{KimPark2004}
Kim H, Park H (2004) Prediction of protein relative solvent accessibility with
  support vector machines and long-range interaction {3D} local descriptor.
\newblock Proteins 54: 557--562.
\bibAnnoteFile{KimPark2004}

\bibitem{NguyenRajapakse2005}
Nguyen MN, Rajapakse JC (2005) Prediction of protein relative solvent
  accessibility with a two-stage {SVM} approach.
\newblock Proteins 59: 30--37.
\bibAnnoteFile{NguyenRajapakse2005}

\bibitem{Levy2010}
Levy ED (2010) A simple definition of structural regions in proteins and its
  use in analyzing interface evolution.
\newblock J Mol Biol 403: 660--670.
\bibAnnoteFile{Levy2010}

\bibitem{Chengetal2006}
Cheng J, Sweredoski MJ, Baldi P (2006) {DOMpro:} protein domain prediction
  using profiles, secondary structure, relative solvent accessibility, and
  recursive neural networks.
\newblock Data Mining and Knowledge Discovery 13: 1--10.
\bibAnnoteFile{Chengetal2006}

\bibitem{ChenZhou2005}
Chen H, Zhou HX (2005) Prediction of solvent accessibility and sites of
  deleterious mutations from protein sequence.
\newblock Nucl Acids Res 33: 3193--3199.
\bibAnnoteFile{ChenZhou2005}

\bibitem{WangDunbrack2003}
Wang G, Dunbrack RL (2003) {PISCES:} a protein sequence culling server.
\newblock Bioinformatics 19: 1589--1591.
\bibAnnoteFile{WangDunbrack2003}

\bibitem{Morrisetal1992}
Morris AL, MacArthur MW, Hutchinson EG, Thornton JM (1992) Stereochemical
  quality of protein structure coordinates.
\newblock Proteins 12: 345--364.
\bibAnnoteFile{Morrisetal1992}

\bibitem{Wolfenden1981}
Wolfenden R, Anderson L, Cullis PM, Southgate CCB (1981) Affinities of amino
  acid side chains for solvent water.
\newblock Biochemistry : 849--855.
\bibAnnoteFile{Wolfenden1981}

\bibitem{Kyte1981}
Kyte J, Doolittle RF (1982) A simple method for displaying the hydropathic
  character of a protein.
\newblock J Mol Biol 157: 105--132.
\bibAnnoteFile{Kyte1981}

\bibitem{Fauchere1983}
Fauchere JL, Pliska VE (1983) Hydrophobic parameters of amino-acid side chains
  from the partitioning of {N-acetyl-amino-acid} amides.
\newblock Eur J Med Chem 18: 369-375.
\bibAnnoteFile{Fauchere1983}

\bibitem{Radzicka1988}
Radzicka A, Wolfenden R (1988) Comparing the polarities of the amino acids:
  side-chain distribution coefficients between the vapor phase, cyclohexane,
  1-octanol, and neutral aqueous solution.
\newblock Biochem 27: 1664--1670.
\bibAnnoteFile{Radzicka1988}

\bibitem{MacCallum2007}
MacCallum JL, Bennett WFD, Tieleman DP (2007) Partitioning of amino acid side
  chains into lipid bilayers: results from computer simulations and comparison
  to experiment.
\newblock J Gen Physiol 129: 371--377.
\bibAnnoteFile{MacCallum2007}

\bibitem{Moon2011}
Moon CP, Fleming KG (2011) Side chain hydrophobicity scales derived from
  transmembrane protein folding into lipid bilayers.
\newblock Proc Natl Acad Sci USA 108: 10174--10177.
\bibAnnoteFile{Moon2011}

\bibitem{Wimley1996}
Wimley WC, Creamer TP, White SH (1996) Solvation energies of amino acid side
  chains and backbone in a family of host-guest pentapeptides.
\newblock Biochem 35: 5109--5124.
\bibAnnoteFile{Wimley1996}

\bibitem{Kabsch1983}
Kabsch W, Sander C (1983) Dictionary of protein secondary structure: pattern
  recognition of hydrogen-bonded and geometrical features.
\newblock Biopolymers 22: 2577--2637.
\bibAnnoteFile{Kabsch1983}

\bibitem{LeeRichards1971}
Lee B, Richards FM (1971) The interpretation of protein structures: estimation
  of static accessibility.
\newblock J Mol Biol 55: 379--400.
\bibAnnoteFile{LeeRichards1971}

\bibitem{KawashimaKanehisa2000}
Kawashima S, Kanehisa M (2000) {AAindex:} amino acid index database.
\newblock Nucleic Acids Res 28: 374.
\bibAnnoteFile{KawashimaKanehisa2000}

\bibitem{TomiiKanehisa1996}
Tomii K, Kanehisa M (1996) Analysis of amino acid indices and mutation matrices
  for sequence comparison and structure prediction of proteins.
\newblock Protein Eng 9: 27--36.
\bibAnnoteFile{TomiiKanehisa1996}

\bibitem{Kawashimaetal2008}
Kawashima S, Pokarowski P, Pokarowska M, Kolinski A, Katayama T, et~al. (2008)
  {AAindex:} amino acid index database, progress report 2008.
\newblock Nucleic Acids Res 36: D202--D205.
\bibAnnoteFile{Kawashimaetal2008}

\bibitem{Laskowskietal1993}
Laskowski RA, MacArthur MW, Moss DS, Thornton JM (1993) {PROCHECK} -- a program
  to check the stereochemical quality of protein structures.
\newblock J App Cryst 26: 283--291.
\bibAnnoteFile{Laskowskietal1993}

\bibitem{Tienetal2013}
Tien MZ, Sydykova DK, Meyer AG, Wilke CO (2013) {PeptideBuilder:} a simple
  {Python} library to generate model peptides.
\newblock PeerJ 1: e80.
\bibAnnoteFile{Tienetal2013}

\end{thebibliography}

@@

\begin{figure}[H]
%\includegraphics[width=4in]{figures/Figure1.pdf}
\caption{\label{fig:BarGraphRSA}Frequency of residues with $\text{RSA}>1$ in empirical protein structures. Nearly all amino acids, and notably R, D, K, G, and P, show $\text{RSA}>1$ 
when RSA is calculated using the normalization values of either Rose \emph{et al.} \cite{Rose1985} or Miller \emph{et al.} \cite{Miller1987}.}
\end{figure}

\begin{figure}[H]
%\includegraphics[width=3in]{figures/Figure2.pdf}
\caption{\label{fig:RamaAla}Ramachandran plot for alanine residues in our empirical data set. Coordinates which correspond to RSA values $>1$ are shown in red and are clearly concentrated around coordinates $(-50^\circ,-45^\circ)$. We therefore propose that this region contains the maximally exposed conformation of alanine and should be used for calculating maximum SA.}
\end{figure}

\begin{figure}[H]
%\includegraphics[width=6in]{figures/Figure3.pdf}
\caption{\label{fig:heatrama} Ramachandran plots for empirical and theoretical maximum SA values of alanine. (A) Empirical maximum SA values for each $5^\circ$ by $5^\circ$ bin. All bins in the ALLOWED region are shown. (B) Theoretical maximum SA values, as determined by computational modeling, shown for non-empty bins in (A). Both the empirical and the theoretical approach find the largest SA values in the $\alpha$-helix region around $(-50^\circ,-45^\circ)$. By contrast, the extended conformation $(-120^\circ, 140^\circ)$ leads to relatively low maximum SA.}
\end{figure}

\begin{figure}[H]
%\includegraphics[width=3in]{figures/Figure4.pdf}
\caption{\label{fig:EvC} Difference between theoretically and empirically determined maximum SA values for alanine, across $5^\circ$ by $5^\circ$ bins. As the amount of data per bin increases, the difference between theoretical and empirical maximum SA approaches zero, demonstrating that our two methods converged with increasing amounts of data. Furthermore, the difference between values is frequently close to zero, even when little data is available for a bin. This observation indicates that our theoretically derived maximum SA values provide a tight bound on the empirically observed ones.}
\end{figure}
